\documentclass[11pt,a4paper]{article}

\usepackage[margin=1cm]{geometry}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{multicol}
\usepackage{wrapfig}
\usepackage{anyfontsize}
\usepackage[dvipsnames]{xcolor}
\usepackage{tikz}
\usepackage{pgf}
\usepackage{multirow}
\usepackage{enumitem}
\usepackage{lmodern}
\usepackage{changepage}
\usepackage{ragged2e}
\usepackage{tcolorbox}
\usepackage{fontawesome}

% font setup
\usepackage[T1]{fontenc}
\usepackage{inter}

\pagenumbering{gobble}
\raggedright

\begin{document}

% HEADER
\begin{center}
    {\huge \textbf{Cody Johnson}}\\[0.5em]
    \small{Vancouver, BC > Calgary, AB} 
\end{center}%
\vspace{1em}
\vspace{5em}


\begin{adjustwidth}{}{}

    To the hiring manager,
    \vspace{2em}
    
    My name is Cody and I'm writing to you regarding the Full Stack Engineering position posted on Linkedin. With extensive experience working in PCI, and eight years of experience building enterprise solutions, I believe I could be a great candidate.
    \vspace{1em}

    My career began in the payment space, aggregating data across the major platforms (including Stripe!). Since then I've worked throughout the web stack, with a brief stint at Electronic Arts working on the build systems responsible for FIFA21. Notably at Treez, I led the development of a data system that ultimately reduced report generation time by over 90\% enabling real-time analytics for our customers. With Skoookum, I've been responsible for the entire tech stack - NATs and private subnets up through React components.
    \vspace{1em}

    I'm enthusiastic, maintain a high standard, and am capable of leading technical projects through ideation and out into the world. I love mentoring juniors and cultivating a team-first mentality. Thank you for your consideration.

\end{adjustwidth}

\vspace{4em}

Cody Johnson\\
\vspace{0.3em}
\scriptsize{Software Engineer}


\vfill

\begin{center}
    \faGlobe\ codyj.io%
    \hspace{1em}\textbar\hspace{1em}%
    \faEnvelope\ codywj777@gmail.com%
    \hspace{1em}\textbar\hspace{1em}%
    \faPhone\ (604) 802-6801%
    \hspace{1em}\textbar\hspace{1em}%
    \faGithub\ github.com/cody-j%
\end{center}


\end{document}
